Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-19 ms.qmd
Going to ditch Southern hemisphere as there isn't too much data there anyway

zoom_areas <- data.frame(
     x = c(-130,  -10, 130),
     y = c(  25, 30, -25),
  xend = c( -50, 45, 170),
  yend = c(  55,  70, -5),
  label = c("North America", "Europe", "Asia")
)

@@

p <- map1_current / (zoom_plots[[1]] | zoom_plots[[2]] | zoom_plots[[3]])

>>>>

zoom_areas <- data.frame(
     x = c(-130, -10, -60, 145),
  xend = c( -50, 48, -35, 155),
     y = c(  25, 30, 0, -45),
  yend = c(  55,  70, -60, -10),
  label = c("North America", "Europe", "South America", "Australia")
)

@@

# Make a multipanel plot. Make teh world_map plot the biggest, and then add the zoomed in plots arond it using pactchwork

p <- (zoom_plots[[1]] | plot_spacer() | zoom_plots[[2]]) / map1_current  + plot_layout(heights  = c(1, 2.5)) + plot_annotation(tag_levels = "A", tag_suffix = ")")

p
